Author Guidelines for DAGM-OAGM Submission

### 2013-08-21 itm/paper.tex
Finish off itm :) - meannn can't run out of the box on mnist.

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lrrrccccc}
\toprule
\multicolumn{4}{c}{Dataset} &\multicolumn{4}{c}{Results}\\
\cmidrule{1-4}
\cmidrule{5-9}
Description &     n &    d &   k &  $k$-Means      & MeanNN        & SL            &   ITM        & ITM ID \\
\cmidrule{1-4}                   \cmidrule{5-5}    \cmidrule{6-6}  \cmidrule{7-7} \cmidrule{8-8} \cmidrule{9-9}
digits      &  1797 &   64 &  10 &     0.62 &      0.67            &0.10          &\B{0.85}       &0.73\\ 
faces       &   400 & 4096 &  40 &     0.41 &      0.49            &0.08          &0.02           &\B{0.54}\\ 
iris        &   150 &    4 &   3 &     0.72 &      0.75            &0.55          &\B{0.88}       &0.88\\
usps        &  9298 &  256 &  10 &     0.52 &      0.54            &0.00          &   0.44        &\B{0.64}\\ 
vehicle     &   846 &   18 &   4 &     0.10 &      0.09            &0.00          &\B{0.10}       &0.10\\
vowel       &   990 &   10 &  11 &     0.17 &      0.19            &0.00          &\B{0.20}       &0.19\\
waveform    &  5000 &   21 &   2 & \B{0.37} &      0.30            &0.00          &   0.23        &0.23\\
mnist       & 70000 &  784 &  10 &     0.37 &      xxx             &0.00          &   0.50        &0.77\\
\bottomrule
\end{tabularx}
\caption{Adjusted Rand Index of $k$-Means, MeanNN, single link agglomerative clustering and
ITM on several datasets (higher is better). The best score for
each dataset is printed in bold.}\label{results}
\end{table}

>>>>

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lrrrccccc}
\toprule
\multicolumn{4}{c}{Dataset} &\multicolumn{4}{c}{Results}\\
\cmidrule{1-4}
\cmidrule{5-9}
Description &     n &    d &   k &  $k$-Means      & MeanNN        & SL            &   ITM        & ITM ID \\
\cmidrule{1-4}                   \cmidrule{5-5}    \cmidrule{6-6}  \cmidrule{7-7} \cmidrule{8-8} \cmidrule{9-9}
digits      &  1797 &   64 &  10 &     0.62 &      0.67            &0.10          &\B{0.85}       &0.73\\ 
faces       &   400 & 4096 &  40 &     0.41 &      0.49            &0.08          &0.02           &\B{0.54}\\ 
iris        &   150 &    4 &   3 &     0.72 &      0.75            &0.55          &\B{0.88}       &0.88\\
usps        &  9298 &  256 &  10 &     0.52 &      0.54            &0.00          &   0.44        &\B{0.64}\\ 
vehicle     &   846 &   18 &   4 &     0.10 &      0.09            &0.00          &\B{0.10}       &0.10\\
vowel       &   990 &   10 &  11 &     0.17 &      0.19            &0.00          &\B{0.20}       &0.19\\
waveform    &  5000 &   21 &   2 & \B{0.37} &      0.30            &0.00          &   0.23        &0.23\\
mnist       & 70000 &  784 &  10 &     0.37 &      N/A$^\dagger$         &0.00          &   0.50        &0.77\\
\bottomrule
\end{tabularx}
\caption{Adjusted Rand Index of $k$-Means, MeanNN, single link agglomerative clustering and
ITM on several datasets (higher is better). The best score for
each dataset is printed in bold.\\$^\dagger$\footnotesize We were unable to make MeanNN scale to 70000 data points, as storing the
whole pairwise distance matrix seems critical.\label{results}}
\end{table}
